### 2020-05-14 Manuscript/manuscript.tex
add NW Laurentia rift details to tectonic history

In northwest Laurentia, the sedimentary rock record is distinct from further south as it also records earlier Neoproterozoic basin development during the Tonian Period in addition to Cryogenian basin development \citep{Macdonald2012a}. Tectonic extension is recorded in units of the lower Fifteenmile Group with maximum depositional ages of ca. 1050 Ma with ongoing basin development ca. 812 Ma (age constraint from a U-Pb zircon date on a tuff within the upper Fifteenmile Group; \citealp{Macdonald2010a}) potentially through thermal subsidence \citep{Macdonald2012a}. Earlier basin development recorded by the Mesoproterozoic/Neoproterozoic Pinguicula Group could provide valuable insight on tectonic history as it has been interpreted to have been deposited in an extensional basin \citep{Medig2016a}, however it is poorly constrained in terms of age -- older than the Fifteenmile Group and younger than the ca. 1382 Ma Hart River sills (which themselves have been interpreted to be emplaced in conjunction with rifting; \citealp{Verbaas2018a}).

>>>>

In northwest Laurentia from the Ogilvie Mountains of Yukon to Victoria Island, the sedimentary rock record is distinct from further south as it also records earlier Neoproterozoic basin development during the Tonian Period in addition to Cryogenian basin development \citep{Macdonald2012a}. Tectonic extension is recorded in units of the lower Fifteenmile Group with maximum depositional ages of ca. 1050 Ma with ongoing basin development ca. 812 Ma (age constraint from a U-Pb zircon date on a tuff within the upper Fifteenmile Group; \citealp{Macdonald2010a}) potentially through thermal subsidence \citep{Macdonald2012a}. Earlier basin development in the region recorded by the Mesoproterozoic/Neoproterozoic Pinguicula Group could provide valuable insight on tectonic history as it has been interpreted to have been deposited in an extensional basin \citep{Medig2016a}, however it is poorly constrained in terms of age -- older than the Fifteenmile Group and younger than the ca. 1382 Ma Hart River sills (which themselves have been interpreted to be emplaced in conjunction with rifting; \citealp{Verbaas2018a}).
